---
title: "Week 6 Quiz"
author: "Johann Wagner - u6958957"
date: "`r Sys.Date()`"
output:
 html_document:
 toc: true
 toc_depth: 4
 theme: cosmo
 number_sections: false
 toc_float: true
 highlight: pygments
 fig_width: 8
 fig_height: 4
---
# Bonus section

## Loading in Tidyverse
The tidyverse is a collection of R packages designed for data science. All packages share a similar design philosophy, grammar, and data structures.Tidyverse includes packages such as: ggplot2, dplyr, tidyr, readr, purr, tibble, stringr, lubriate, and forcats.

https://www.tidyverse.org/

```{r, warning = FALSE}
library(tidyverse)
library(skimr)

```

## Loading the data

```{r}
raw_data <- read_csv("raw_data/data.csv")
```

## Exploratory Data Analysis

```{r}
raw_data %>% skim()
```

It seems like there is one categorical variable called Sex with two unique values (most likely male and female) and a variety of continous and integer data. Two variables have missing data.

## An interesting plot

Let's compare the distribution of weight between both sex.

```{r}
raw_data %>% 
        ggplot(aes(x = Sex,
                   y = weight,
                   colour = Sex)) +
        geom_violin() +
        geom_jitter(
                alpha = 0.5
        )
```

